---
title: "ToothGrowth"
author: "EGB"
date: "May 29, 2016"
output: html_document
---

This document will provide some exploratory data analysis with the ToothGrowth data in the R datasets library and some confidence iterval and/or hypothesis testing along with their subsequent conclusions.

#ToothGrowth Data

```{r}
library(datasets)
str(ToothGrowth)
```

#Exploratory Plot

```{r, echo=FALSE}
library(ggplot2)
qplot(dose, len, data = ToothGrowth, color = supp)
```

#95% Confidence Intervals

```{r}
ML = mean(ToothGrowth$len)
ML
n = 60
ML + c(-1,1)*qnorm(.975)*sd(ToothGrowth$len)/sqrt(n)
```


#Hypothesis Testing

Null hypothesis, H0 is that the mean of tooth growth is ML (18.81333)

##Tooth growth by Supp
###Supp - OJ

```{r}
MLO = mean(ToothGrowth$len[ToothGrowth$supp=="OJ"])
MLO
```

###Supp - VC

```{r}
MLV = mean(ToothGrowth$len[ToothGrowth$supp=="VC"])
MLV
```

Since both values are between the 95% confidence interval, we can still assume our Null hypothesis is true

##Tooth growth by Dose
###Dose - 0.5

```{r}
MLD = mean(ToothGrowth$len[ToothGrowth$dose==0.5])
MLD
```

###Dose - 1.0

```{r}
MLD1 = mean(ToothGrowth$len[ToothGrowth$dose==1.0])
MLD1
```

###Dose - 2.0

```{r}
MLD2 = mean(ToothGrowth$len[ToothGrowth$dose==2.0])
MLD2
```

Both the 0.5 and 2.0 dose means are out of our 95% confidence interval.  Because that is two out of the three dose values, I would think our null hypothesis needs to be further examined.